%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,roman,colorlinks,urlcolor=teal,linkcolor=teal]{moderncv}
%teal % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
%\usepackage[lining]{libertine}
\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{enumitem,etaremune,amsfonts}
\setlist{labelsep=1em}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
%\usepackage[colorlinks=true,allcolors = blue]{hyperref}
\usepackage[scale=0.9]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3.2cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Kang} % Your first name
\familyname{Lu}
% All information in this block is optional, comment out any lines you don't need

\address{Department of Mathematics}{University of Virginia}
%\mobile{+91-7730853210}
\email{Kang.Lu@Virginia.edu}
\extrainfo{
	\httplink{kanglu.me}
}

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Employment}

\cventry{Aug 2022--Present}{Mary Ann Pitts Research Associate and Lecturer}{\textsc{University of Virginia}}{}{}{Mentor: \href{https://uva.theopenscholar.com/weiqiang-wang/}{Weiqiang Wang}}

\cventry{Sep 2020--Jul 2022}{Visiting Assistant Professor}{\textsc{University of Denver}}{}{}{Mentor: \href{https://cs.du.edu/~alinshaw/}{Andrew Linshaw}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2014--2020}{Ph.D. in Mathematics}{Indiana University Purdue University Indianapolis}{}{}{Advisors: \href{https://science.iupui.edu/people-directory/people/mukhin-evgeny.html}{Evgeny Mukhin} \& \href{https://science.iupui.edu/people-directory/people/tarasov-vitaly.html}{Vitaly Tarasov}}

\cventry{2012--2014}{M.S. in Mathematics}{Zhejiang University}{}{}{Advisor: Gang Han}

\cventry{2006--2010}{B.S. in Mathematics}{Fudan University}{}{}{Advisor: Meng Chen}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Research Interests}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Representation Theory}{Quantum Algebras}
\cvlistdoubleitem{Mathematical Physics}{Integrable Systems}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Publications}

\begin{etaremune}[leftmargin=1cm]
\item \underline{Kang Lu}, {\textit{On Bethe eigenvectors and higher transfer matrices for supersymmetric spin chains}}, \href{https://doi.org/10.1007/JHEP04(2023)120}{J. High Energ. Phys.} \textbf{04} (2023), Article number: 120.
% \item Kang Lu, {\textit{Completeness of Bethe ansatz for Gaudin models with $\mathfrak{gl}(1|1)$
% symmetry and diagonal twists}}, \href{https://www.mdpi.com/2073-8994/15/1/9}{Symmetry} \textbf{15} (2023), no. 1, 9.
\item \underline{Kang Lu}, {\textit{Schur-Weyl duality for quantum toroidal superalgebras}}, \href{https://doi.org/10.1016/j.jpaa.2023.107382}{J. Pure Appl. Algebra} \textbf{227} (2023), no. 9, 107382.

\item \underline{Kang Lu}, {\textit{Completeness of Bethe ansatz for Gaudin models associated with} $\mathfrak{gl}(1|1)$}, \href{https://www.sciencedirect.com/science/article/pii/S0550321322001419}{Nuclear Phys. B} \textbf{980} (2022), 115790.

\item \underline{Kang Lu}, {\textit{A note on odd reflections of super Yangian and Bethe ansatz}}, \href{https://link.springer.com/article/10.1007/s11005-022-01524-3}{Lett. Math. Phys.} \textbf{112} (2022), Article no.: 29.

\item \underline{Kang Lu}, {\textit{Gelfand-Tsetlin bases for representations of super Yangian and quantum affine superalgebra}}, \href{https://link.springer.com/article/10.1007/s11005-021-01488-w}{Lett. Math. Phys.} \textbf{111} (2021), Article no.: 145.

\item \underline{Kang Lu} and Evgeny Mukhin, {\textit{Bethe ansatz equations for orthosymplectic Lie superalgebras and self-dual superspaces}}, \href{https://doi.org/10.1007/s00023-021-01091-8}{Ann. Henri Poincar\'{e}} \textbf{22} (2021), no. 12, 4087--4130.

\item \underline{Kang Lu} and Evgeny Mukhin, {\textit{Jacobi-Trudi identity and Drinfeld functor for super Yangian}}, \href{https://dx.doi.org/10.1093/imrn/rnab023}{Int. Math. Res. Not. IMRN} \textbf{2021} (2021), no. 21, 16749-16808.

\item \underline{Kang Lu} and Evgeny Mukhin, {\textit{On the supersymmetric XXX spin chains associated to} $\mathfrak{gl}_{1|1}$}, \href{https://dx.doi.org/10.1007/s00220-021-04155-2}{Commun. Math. Phys.} \textbf{386} (2021), 711-747.

\item \underline{Kang Lu}, \textit{Perfect integrability and Gaudin models}, \href{https://www.emis.de/journals/SIGMA/2020/132/}{SIGMA} \textbf{16} (2020), 132, 10 pages.
  
\item Chenliang Huang, \underline{Kang Lu}, and Evgeny Mukhin, {\textit{Solutions of $\mathfrak{gl}_{m|n}$ XXX Bethe ansatz equation and rational difference operators}}, \href{https://doi.org/10.1088/1751-8121/ab1960}{J. Phys. A: Math. Theor.} \textbf{52} (2019), no. 37, 375204, 31 pages.	
			
\item \underline{Kang Lu} and Evgeny Mukhin, {\textit{On the Gaudin model of type G$_2$}}, \href{https://doi.org/10.1142/S0219199718500128}{Commun. Contemp. Math.} \textbf{21} (2019), no. 3, 1850012, 31 pages.

\item Gang Han, Yucheng Liu, and \underline{Kang Lu}, {\textit{Multiplicity free gradings on semisimple Lie and Jordan algebras and skew root systems}}, \href{https://doi.org/10.1142/S1005386719000129}{Algebra Colloq.} {\textbf{26}} (2019), no. 1, 123--138.
			
\item \underline{Kang Lu}, {\textit{Lower bounds for numbers of real self-dual spaces in problems of Schubert calculus}}, \href{https://doi.org/10.3842/SIGMA.2018.046}{SIGMA} {\textbf{14}} (2018), 046, 15 pages.	
			
\item \underline{Kang Lu}, Evgeny Mukhin, and Alexander Varchenko, 
			{\textit{Self-dual Grassmannian, Wronski map, and representations of} $\mathfrak{gl}_N$, $\mathfrak{sp}_{2r}$, $\mathfrak{so}_{2r+1}$}, \href{http://dx.doi.org/10.4310/PAMQ.2017.v13.n2.a4}{Pure Appl. Math. Q.} {\textbf{13}} (2017), no.2, 291--335, special issue in honor of Yuri Manin's 80-th birthday.
					
\item \underline{Kang Lu}, Evgeny Mukhin, and Alexander Varchenko, 
			{\textit{On the Gaudin model associated to Lie algebras of classical types}}, \href{https://doi.org/10.1063/1.4964389}{J. Math. Phys.} {\textbf{57}} (2016), no. 10, 101703, 23 pages.
	    \end{etaremune}
	    
\section{Preprints}

\begin{enumerate}[leftmargin=1.17cm]


% \item Kang Lu, E. Mukhin, V. Tarasov,
% {\textit{TBA}}, in preparation.
\item \underline{Kang Lu}, {\textit{Isomorphism between twisted $q$-Yangians and affine $\imath$quantum groups: type AI}}, \href{https://arxiv.org/abs/2308.12484}{arXiv:2308.12484}. 

\item \underline{Kang Lu}, Weiqiang Wang, and Weinan Zhang, {\textit{A Drinfeld type presentation of twisted Yangians}}, \href{https://arxiv.org/abs/2308.12254}{arXiv:2308.12254}. 

\item \underline{Kang Lu}, {\textit{Twisted super Yangians of type AIII and their representations}}, \href{https://arxiv.org/abs/2311.16373}{arXiv:2311.16373}.

\item \underline{Kang Lu}, Weiqiang Wang, and Weinan Zhang, {\textit{Affine $\imath$quantum groups and twisted Yangians in Drinfeld presentations}}, in preparation.

\item \underline{Kang Lu} and Weiqiang Wang, {\textit{GKLO type representations for twisted Yangians and affine $\imath$quantum groups}}, in preparation.





% \item Kang Lu, Gang Han, and Jun Yu, {\it Fine gradings of complex simple Lie algebras and Finite Root Systems}, preprint, \href{https://arxiv.org/abs/1410.7945}{arXiv:1410.7945}. 

\end{enumerate}

	    
\section{Teaching}

\hskip 3.5 cm \textbf{University of Virginia}
\vskip 0.2cm 
\cvitem{2024 Spring}{MATH 2310: Calculus III}
\cvitem{2023 Spring}{MATH 3351: Elementary Linear Algebra}
\cvitem{2022 Fall}{MATH 3310: Basic Real Analysis}

\hskip 3.5 cm \textbf{University of Denver}
\vskip 0.2cm 
\cvitem{2022 Summer}{MATH 1952: Calculus II}
\cvitem{2022 Spring}{MATH 2070: Introduction to Differential Equations}
\cvitem{2022 Spring}{MATH 2080: Calculus of Several Variables}
\cvitem{2022 Winter}{MATH 1951: Calculus I}
\cvitem{2022 Winter}{MATH 1150: Mathematics for Cryptography}
\cvitem{2021 Autumn}{MATH 1951: Calculus I}
\cvitem{2020 Spring}{MATH 1952: Calculus II}
\cvitem{2020 Winter}{MATH 1150: Introduction to Cryptography}
\cvitem{2020 Winter}{MATH 2070: Introduction to Differential Equations}
\cvitem{2020 Autumn}{MATH 1951: Calculus I}

\hskip 3.5 cm \textbf{Indiana University Purdue University Indianapolis}
\vskip 0.2cm 
\cvitem{2020 Summer}{MATH 16500: Calculus and Analytic Geometry I}
\cvitem{2020 Spring}{MATH 22100: Calculus for Technology I}
\cvitem{2019 Fall}{MATH 15400: Trigonometry}
\cvitem{2019 Summer}{MATH 26600: Ordinary Differential Equations}
\cvitem{2019 Spring}{MATH 22100: Calculus for Technology I} 
\cvitem{2018 Fall}{MATH 11100: Intermediate algebra}
\cvitem{2018 Summer}{MATH 15400: Trigonometry} 
\cvitem{2018 Spring}{MATH 11000: Fundamentals of Algebra} 
\cvitem{2017 Fall}{MATH 16500: Calculus and Analytic Geometry I, (Recitation)}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Mentoring and Services}
\cventry{Oct 2023--Present}{14th Southeastern Lie Theory Workshop 
}{\textsc{University of Virginia}}{Co-organizer}{}{}
\cventry{Sep 2023--Present}{Undergraduate directed reading}{Convex optimization and machine learning}{Mentor}{\textsc{University of Virginia}}{Mentee: Alex Ning}
\cventry{Aug 2023--Present}{Algebra Seminar}{Co-organizer}{\textsc{University of Virginia}}{}{}

\section{Referee Services}
\begin{itemize}[parsep=-0.2em, leftmargin=3.55cm]
    \item Algebras and Representation Theory $(\times 2)$
    % \item Applied Sciences
    \item Arnold Mathematical Journal
    \item Communications in Mathematical Physics $(\times 2)$
    \item Compositio Mathematica
    \item International Mathematics Research Notices
    \item Journal of Algebra
    \item Journal of Mathematical Physics $(\times 2)$
    \item Journal de l'École polytechnique - Mathématiques
    \item Letters in Mathematical Physics
    % \item Mathematics $(\times 14)$
    \item SciPost Physics
    \item SIGMA $(\times 2)$
    % \item Symmetry $(\times 10)$
    \item Transformation Groups $(\times 2)$
\end{itemize}

% Algebras and Representation Theory $(\times 2)$, 
% Arnold Mathematical Journal,
% Communications in Mathematical Physics $(\times 2)$,
% Compositio Mathematica,
% International Mathematics Research Notices,
% Journal of Algebra,
% Journal of Mathematical Physics $(\times 2)$,
% Journal de l'École polytechnique - Mathématiques,
% Letters in Mathematical Physics,
% SciPost Physics,
% SIGMA $(\times 2)$,
% Transformation Groups $(\times 2)$


\section{Invited Talks}
\cventry{Mar 1-3, 2024}{14th Southeastern Lie Theory Workshop}{University of Virginia}{Charlottesville}{VA}{}
\cventry{Jan 29-31, 2024}{Physical Mathematics and Beyond Workshop}{Korea Institute For Advanced Study}{Seoul}{South Korea}{\textcolor{red}{Canceled due to visa issue}}
\cventry{Nov 29, 2023}{Online Talk via TencentMeeting}{Yunnan University of Finance and Economics}{Kunming, Yunnan}{China}{Talk: Representations of twisted Yangians of type AIII}
\cventry{May 12-14, 2023}{13th Southeastern Lie Theory Workshop}{North Carolina State University}{Raleigh}{NC}{Talk: A Drinfeld presentation of twisted Yangians}
\cventry{Apr 26, 2023}{Algebra Seminar}{University of Virginia}{Charlottesville}{VA}{Talk: A Drinfeld presentation of twisted Yangians}
\cventry{Mar 13-14, 2021}{2021 AMS Spring Southeastern Sectional Meeting}{Special Session on Superalgebras, Quantum Groups, and Related Topics}{}{}{Talk: Skew representations of super Yangian}
\cventry{Nov 19, 2021}{NCTS Seminar on Representation Theory}{Taiwan}{Zoom}{}{Talk: Representations of Super Yangian}
\cventry{Mar 11, 2021}{Rocky Mountain Representation Theory Seminar}{Zoom}{}{}{Talk: Skew representations of super Yangian}
\cventry{Feb 17, 2021}{Representations and Lie Theory seminar}{Ohio State University}{Zoom}{}{Talk: Skew representations of super Yangian}
\cventry{Oct 19, 2020}{Algebra and Logic Seminar}{University of Denver}{Denver}{CO}{Talk:  Gaudin model, Feigin-Frenkel center, and Grassmannian}
\cventry{Apr 4-5, 2020}{2020 AMS Spring Central Sectional Meeting}{Purdue University}{West Lafayette}{IN}{\textcolor{red}{Canceled due to COVID-19}}
\cventry{Nov 15, 2019}{Algebra Seminar}{University of Virginia}{Charlottesville}{VA}{Talk: Jacobi-Trudi identity, Berezinian, and transfer matrices}
\cventry{Oct 04, 2019}{Physically inspired mathematics seminar}{University of North Carolina}{Chapel Hill}{NC}{Talk: Supersymmetric quantum spin chains}
\cventry{Apr 13-14, 2019}{2019 AMS Spring Eastern Sectional Meeting}{University of Connecticut}{Hartford}{CT}{Talk: On the supersymmetric XXX spin chain associated to $\mathfrak{gl}_{1|1}$}
\cventry{Mar 15-17, 2019}{2019 AMS Spring Southeastern Sectional Meeting}{Auburn University}{Auburn}{AL}{Talk: Self-dual Grassmannian and Representations of $\mathfrak{gl}_N$, $\mathfrak{sp}_{2r}$, and $\mathfrak{so}_{2r+1}$}
\cventry{Apr 1-2, 2017}{2017 AMS Spring Central Sectional Meeting}{Indiana University}{Bloomington}{IN}{Talk: Bethe ansatz method in Gaudin Model}

\section{Presentations}
\cventry{Apr 15-16, 2023}{2023 AMS Spring Central Sectional Meeting}{Special Session on Representation Theory, Geometry and Mathematical Physics}{University of Cincinnati}{OH}{Talk: Representations of twisted super Yangians of type AIII}
\cventry{Jan 15-18, 2020}{Joint Mathematics Meetings 2020}{Colorado Convention Center}{Denver}{CO}{Talk: On the supersymmetric XXX spin chains}
\cventry{Aug 12-16, 2019}{Representation Theory and Integrable Systems}{ETHZ}{Zurich}{Switzerland}{Contributed Talk: On the supersymmetric XXX spin chain associated to $\mathfrak{gl}_{1|1}$}
\cventry{May 29-Jun 2, 2017}{Representation Theory at the Crossroads of Modern Mathematics}{Universit\'{e} de Reims Champagne Ardenne}{Reims}{France}{Poster: Self-dual Grassmannian and Representations of $\mathfrak{gl}_N$, $\mathfrak{sp}_{2r}$, and $\mathfrak{so}_{2r+1}$}


\section{Participation in Conferences
and Workshops}
\cventry{May 27-31, 2024}{Representation Theory and Related Geometry: Progress and Prospects}{University of Georgia}{GA}{}{} 
\cventry{Mar 4-5, 2024}{Randomness and Lie-theoretic structures}{University of Virginia}{VA}{}{} 
\cventry{Nov 17-19, 2023}{Workshop on Geometric Representation Theory and Moduli spaces}{University of North Carolina at Chapel Hill}{NC}{}{} 
\cventry{Jun 4-8, 2018}{Representation Theory, Mathematical Physics and Integrable Systems}{Centre International de Rencontres Mathématiques}{Luminy}{France}{}
\cventry{Jun 6-9, 2017}{Algebraic Analysis}{IHÉS}{Bures-sur-Yvette}{France}{}
\cventry{Apr 30, 2016}{Algebra, Geometry and Combinatorics Day}{University of Notre Dame}{Notre Dame}{IN}{}
\cventry{Aug 14-18, 2015}{Lie Algebras, Vertex Operator Algebras, and Related Topics}{University of Notre Dame}{Notre Dame}{IN}{}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{References}
\cventry{}{\href{https://cas.uoregon.edu/directory/natural-sciences/all/brundan}{Jonathan Brundan}}{University of Oregon}{Department of Mathematics}{Brundan@uoregon.edu}{}
\cventry{}{\href{https://cs.du.edu/~alinshaw/}{Andrew Linshaw}}{University of Denver}{Department of Mathematics}{Andrew.Linshaw@du.edu}{}
\cventry{}{\href{https://science.iupui.edu/people-directory/people/mukhin-evgeny.html}{Evgeny Mukhin}}{Indiana University Purdue University Indianapolis}{Department of Mathematical Science}{emukhin@iupui.edu}{}
\cventry{}{\href{https://science.iupui.edu/people-directory/people/tarasov-vitaly.html}{Vitaly Tarasov}}{Indiana University Purdue University Indianapolis}{Department of Mathematical Science}{vtarasov@iupui.edu}{}
\cventry{}{\href{https://varchenko.web.unc.edu/}{Alexander Varchenko}}{University of North Carolina at Chapel Hill}{Department of Mathematics}{anv@email.unc.edu}{}
\cventry{}{\href{https://uva.theopenscholar.com/weiqiang-wang/}{Weiqiang Wang}}{University of Virginia}{Department of Mathematics}{ww9c@virginia.edu}{}

\end{document}